---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---


```{r}
library(here)
library(dplyr)
library(readxl)
library(ggplot2)
library(openxlsx)
```


### Cognitive domains
  
Memory

  - sum(N_VATA1, N_VATA2)
  - sum(N_15WT1, N_15WT2, N_15WT3, N_15WT4, N_15WT5)
  - N_15WTui

  
Executive

  - N_CRach
  - N_Strt3
  - N_TMTBt
  - sum(N_FLD, N_FLA, N_FLT)


Steps to calculate domain scores:

- Deal with 997, 998, 999 NA scores in all tests that we use
- Check for impossible values of 0, changed to NA (for TMTB and Stroop tests)
- Introduce time cutoffs for Stroop and TMT tests
- Sum some scores to create summed tests
- z-score with respect to mean and sd of the reference group
- invert scores so that higher values mean better performance
- create composite domains (if at least 2 tests available per domain)



```{r}
dat <- readxl::read_excel(here("data", "raw","551_cog_reserve_activity_DBo_20230424_Long.xlsx"), col_names = T)
dat2 <- readxl::read_excel(here("data", "raw","551_cog_reserve_activity_DBo_20231124_Long.xlsx"), col_names = T)

cogtests <- c("N_VATA1", "N_VATA2",
              "N_15WT1", "N_15WT2", "N_15WT3", "N_15WT4", "N_15WT5",
              "N_15WTui", 
              
              "N_CRach",
              "N_Strt3",
              "N_TMTBt",
              "N_FLD", "N_FLA", "N_FLT"
              )

dat %>%
  select(cogtests) %>% 
  psych::describe(.)

```


```{r}
# Deal with 997, 998, 999 NA scores in all tests that we use

# Convert 997, 998 and 999 to NA in the NPO file
# From Juhan's P2 code:
#   999 aborted, patient doesn't understand instructions
#   998 aborted, patient refuses test
#   997 not administered
# 9999 etc. for typos

dat <- dat %>% 
  mutate(across(all_of(cogtests), ~ifelse(. %in% c(999, 9999), NA, .))) %>% 
  mutate(across(all_of(cogtests), ~ifelse(. %in% c(998, 9998), NA, .))) %>% 
  mutate(across(all_of(cogtests), ~ifelse(. %in% c(997, 9997), NA, .))) %>% 
  mutate(V_MMSE = ifelse(V_MMSE %in% c(999, 99), NA, V_MMSE))


dat %>%
  select(cogtests) %>% 
  psych::describe(.)

```

```{r}
  
# Check for impossible values of 0, change to NA (for TMTA, TMTB or Stroop tests) 
dat <- dat %>% mutate (N_TMTBt = ifelse(N_TMTBt == "0", NA, N_TMTBt),
                       N_Strt3 = ifelse(N_Strt3 == "0", NA, N_Strt3)
                       )

# Introduce time cutoffs for Stroop and TMT tests
dat <- dat %>% mutate (N_TMTBt = ifelse(N_TMTBt > 500, 500, N_TMTBt),
                       N_Strt3 = ifelse(N_Strt3 > 500, 500, N_Strt3))

# Sum  scores to create summed tests
dat <- dat %>% 
  mutate (VATAtot = N_VATA1 + N_VATA2,
          W15Ttot = N_15WT1 + N_15WT2 + N_15WT3 + N_15WT4 + N_15WT5,
          FLDAT = N_FLD + N_FLA + N_FLT)


# z-score each test
# invert scores so that higher values mean better performance

# z-score with respect to mean and sd of the reference group (import values of reference group)
cu_tests <- read.csv(here("data", "raw", "NPO_reference_group_descriptives.csv"), row.names = 1) 


dat <- dat %>% mutate (#Memory
                       Z_VATAtot = (VATAtot - cu_tests["VATAtot", "Mean"]) / cu_tests["VATAtot", "SD"] ,        
                       Z_W15Ttot = (W15Ttot - cu_tests["W15Ttot", "Mean"]) / cu_tests["W15Ttot", "SD"],
                       Z_N_15WTui  = (N_15WTui - cu_tests["N_15WTui", "Mean"]) / cu_tests["N_15WTui", "SD"],
                       
                       #Executive
                       Z_N_CRach = (N_CRach - cu_tests["N_CRach", "Mean"]) / cu_tests["N_CRach", "SD"], 
                       Z_N_Strt3 = (N_Strt3 - cu_tests["N_Strt3", "Mean"]) / cu_tests["N_Strt3", "SD"] *-1,
                       Z_N_TMTBt = (N_TMTBt - cu_tests["N_TMTBt", "Mean"]) / cu_tests["N_TMTBt", "SD"] *-1,
                       Z_FLDAT = (FLDAT - cu_tests["FLDAT", "Mean"]) / cu_tests["FLDAT", "SD"]
                      )

```


```{r}
# Check z-scored test histograms

z_tests <- names(dat)[grepl("Z_", names(dat))]

# #Check which tests are skewed
library(tidyr)
dat %>%
  select(all_of(z_tests)) %>%
  #keep(is.numeric) %>%
  tidyr::gather() %>%
  ggplot(aes(value)) +
    facet_wrap(~ key, scales = "free") +
    geom_histogram()

```


```{r}
# Ensure all tests go in same direction

dat %>%
  select(all_of(z_tests)) %>%
  cor(., method = "pearson", use = "complete.obs")

```



```{r}
# create composite domains (if at least 2 tests available per domain)

### Count available tests for every domain composite score, for creating z-scores. the function adds 1 for every test score not NA per cog domain 
dat$n_mem <- 0
dat$n_exec <- 0

count_available_tests <- function (x,y) (ifelse(!is.na(x), y+1, y+0))

dat$n_mem <- mapply(count_available_tests, dat$Z_VATAtot, dat$n_mem)
dat$n_mem <- mapply(count_available_tests, dat$Z_W15Ttot, dat$n_mem)
dat$n_mem <- mapply(count_available_tests, dat$Z_N_15WTui, dat$n_mem)

dat$n_exec <- mapply(count_available_tests, dat$Z_N_CRach, dat$n_exec)
dat$n_exec <- mapply(count_available_tests, dat$Z_N_Strt3, dat$n_exec)
dat$n_exec <- mapply(count_available_tests, dat$Z_N_TMTBt, dat$n_exec)
dat$n_exec <- mapply(count_available_tests, dat$Z_FLDAT, dat$n_exec)


            
## Calculate final composite scores. Add up for every non-NA value and divide by the number of tests per patient
              
dat <- dat %>% mutate (Z_MEM = ((ifelse(is.na(Z_VATAtot), 0, Z_VATAtot)) + 
                                  (ifelse(is.na(Z_W15Ttot), 0, Z_W15Ttot))+ 
                                  (ifelse(is.na(Z_N_15WTui), 0, Z_N_15WTui))) / n_mem,
                      
                       Z_EXEC = ((ifelse(is.na(Z_N_CRach), 0, Z_N_CRach)) + 
                                   (ifelse(is.na(Z_N_Strt3), 0, Z_N_Strt3)) + 
                                   (ifelse(is.na(Z_N_TMTBt), 0, Z_N_TMTBt)) +
                                   (ifelse(is.na(Z_FLDAT), 0, Z_FLDAT))) / n_exec)

dat <- dat %>% mutate(Z_MEM = ifelse(n_mem <2, NA, Z_MEM),
                      Z_EXEC = ifelse(n_exec <2, NA, Z_EXEC)
                      )

```


#### Domain score distributions

```{r}
domains <-c("V_MMSE", "Z_MEM", "Z_EXEC")

library(tidyr)
dat %>%
  select(all_of(domains)) %>%
  tidyr::gather() %>%
  ggplot(aes(value)) +
    facet_wrap(~ key, scales = "free") +
    geom_histogram()
```


```{r}

dat %>% 
  select(I_ID, N_date, n_mem, n_exec, Z_MEM, Z_EXEC) %>% 
  write.xlsx(., here("data", "interim", "551_cog_reserve_activity_DBo_20230424_Long_Domains.xlsx"))

```








